Full Title

### 2019-10-15 fracGC/p.tex
comonad for pointed types

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A Comonad for Pi}

\newcommand{\alt}{~|~}
\newcommand{\inlv}[1]{\ensuremath{\mathit{inl}(v)}}
\newcommand{\inrv}[1]{\ensuremath{\mathit{inr}(v)}}
\newcommand{\pointed}[2]{[#1 \bullet #2]}

Plain Pi over finite types:
\[\begin{array}{lrcl}
\textit{Value types} & t &::=& 0 \alt 1 \alt t+t \alt t*t \\
\textit{Values}      & v &::=& \star \alt \inlv{v} \alt \inrv{v} \alt (v,v) \\
\textit{Level-1 types} &&& t \leftrightarrow t \\
\textit{Level-1 programs} & c &::=& \cdots \\
\textit{Level-2 types} &&& c \Leftrightarrow c \\
\textit{Level-2 programs} & \alpha &::=& \cdots 
\end{array}\]

Now we define pointed types $\pointed{t}{v}$ which are a record
consisting of a value type together with a value of that type. Both
the level-1 and level-2 program lift naturally to the world of pointed
types but instead of manually rewriting everything we use the fact
that pointed types form a comonad. So for example, given a level-1
program we should be able to just use \textsf{extend} to compose
instead of plain composition of combinators??

Then we can define $\eta$ and $\epsilon$ in the comonadic world.
